A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-30 ICLP Paper/samplepaper.tex
changing the place where to mention dynamic job-based strategies in experiments sections

In addition to assessing decompositions in a purely Job-based fashion,
we have encoded \emph{Machine-based} decompositions \emph{M-EST} and \emph{M-MTRW} in which an operation from a bottleneck machine with the greatest sum of processing times for yet unordered operations is considered next.
For our example instance, the sum of processing times for operations 
is~\lstinline{12}, \lstinline{15}, or again \lstinline{12}, respectively,
for the machines~\lstinline{1}, \lstinline{2}, and~\lstinline{3}.
Hence, the operation to be inserted into the total order first is picked from
machine~\lstinline{2}, where the smallest M-EST or greatest M-MTWR value is
used for choosing a particular job/operation.
Unlike Job-based decompositions, this may lead to the choice of an operation
such that predecessor operations processed by other machines are yet unordered.
In this case, they are inserted into the total order directly before the
operation from a bottleneck machine, and all machine loads are reduced by processing times before determining the next machine to consider.

@@

    % \\[-2.75mm]
    \botline% \hline
    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}
%
In Table~\ref{tab:Table02}, we provide a comparison of the Job- and Machine-based EST and MTWR approaches with %, providing the baseline abbreviated by M-EST.
%Further decomposition strategies are denoted by M-MTWR for the static Machine-based MTWR variant, 
dynamic versions of M-EST$^\text{\,d}$ and M-MTWR$^\text{\,d}$ that
determine M-EST and M-MTWR values w.r.t.\ partial schedules from previous time windows.
\ksverify{We excluded the dynamic variants of Job-based strategies, since they performed worse than their static originals.}
%, as well as static Job-based counterparts J-EST and J-MTWR in the first two rows.
For each decomposition strategy and JSP instance size, we present results for the number
of time windows,
which amounts to the next greater integer of the average number of interrupted optimization
runs in columns headed by Ints, leading to the shortest average makespan.
The considerably increased average makespans in the first two rows clearly indicate that
time windows determined with Job-based decomposition strategies are less adequate than
those investigating bottleneck machines in the first place, and then picking their operations
based on the smallest EST or greatest MTWR value as a secondary criterion.
While Machine-based decomposition turns out to be advantageous,
there is no clear gap between the static M-EST and M-MTWR variants as well as their dynamic
versions M-EST$^\text{\,d}$ and M-MTWR$^\text{\,d}$.
That is, the heuristic to schedule operations from highly loaded machines
as soon as possible works well for decomposing the considered JSP instances,
yet further solution quality differences due to minor deviations in the
decomposition strategy or optimization performance of \clingodl are negligible.

>>>>

Beyond partitioning operations in a purely Job-based fashion,
we have encoded \emph{Machine-based} decompositions \emph{M-EST} and \emph{M-MTRW} in which an operation from a bottleneck machine with the greatest sum of processing times for yet unordered operations is considered next.
For our example instance, the sum of processing times for operations 
is~\lstinline{12}, \lstinline{15}, or again \lstinline{12}, respectively,
for the machines~\lstinline{1}, \lstinline{2}, and~\lstinline{3}.
Hence, the operation to be inserted into the total order first is picked from
machine~\lstinline{2}, where the smallest M-EST or greatest M-MTWR value is
used for choosing a particular job/operation.
Unlike Job-based decompositions, this may lead to the choice of an operation
such that predecessor operations processed by other machines are yet unordered.
In this case, they are inserted into the total order directly before the
operation from a bottleneck machine, and all machine loads are reduced by processing times before determining the next machine to consider.

@@

    % \\[-2.75mm]
    \botline% \hline
    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}
%
In Table~\ref{tab:Table02}, we provide a comparison of the Job- and Machine-based EST and MTWR approaches with %, providing the baseline abbreviated by M-EST.
%Further decomposition strategies are denoted by M-MTWR for the static Machine-based MTWR variant, 
dynamic versions of M-EST$^\text{\,d}$ and M-MTWR$^\text{\,d}$ that
determine M-EST and M-MTWR values w.r.t.\ partial schedules from previous time windows.
% \ksverify{We excluded the dynamic variants of Job-based strategies, since they performed worse than their static originals.}
%, as well as static Job-based counterparts J-EST and J-MTWR in the first two rows.
For each decomposition strategy and JSP instance size, we present results for the number
of time windows,
which amounts to the next greater integer of the average number of interrupted optimization
runs in columns headed by Ints, leading to the shortest average makespan.
The considerably increased average makespans in the first two rows clearly indicate that
time windows determined with Job-based decomposition strategies are less adequate than
those investigating bottleneck machines in the first place, and then picking their operations
based on the smallest EST or greatest MTWR value as a secondary criterion.
While Machine-based decomposition turns out to be advantageous,
there is no clear gap between the static M-EST and M-MTWR variants as well as their dynamic
versions M-EST$^\text{\,d}$ and M-MTWR$^\text{\,d}$\ksverify{,
and the same indifference applies to Job-based decomposition strategies whose dynamic counterparts are thus omitted}.
That is, the heuristic to schedule operations from highly loaded machines
as soon as possible works well for decomposing the considered JSP instances,
yet further solution quality differences due to minor deviations in the
decomposition strategy or optimization performance of \clingodl are negligible.
